Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-29 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:29	22:12:39	(Sat29.Aug)

\begin{figure*}[t]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic_bounds_lca_windows_beta.pdf}%
\caption{$\beta$-values of the windows LCA selects for each image pixel. The underlying image is the same cross as shown in \Fig{oversampling_mosaic_bounds}. Oversampled image, 19x20 windows.}\label{oversampling_mosaic_bounds_beta}
\end{figure*}

@@

@@

Adaptive beamformers process each pixel in a different way in an attempt to surpass the conventional limit of resolution and noise suppression. This non-linear processing of the image increases its bandwidth and introduces a need for oversampling. For MVDR often a factor 10 lateral oversampling is often needed to ensure spatial shift-invariance in source amplitude~\cite{Asen2014}. To ensure that no

@@

\begin{itemize}
\item \emph{Window function}. Frequency responses of typical windows chosen by MVDR in shadow, speckle and highlight regions in an image is shown in \Fig{mvdr_selected_windows}. The responses tend to be symmetric, minimally steered and have slightly varying mainlobe width and sidelobe suppression. We use Kaiser windows to mimic these responses.
\item \emph{Window parameters}. The Kaiser window parameter $\beta$ adjusts the compromise between resolution and sidelobe suppression. At $\beta=0$ it yields a rectangular window, and at and $\phi$ controls the amount of steering.. $\beta=0$ ) and a gaussian curve (
\end{itemize}

>>>>

\setcounter{dbltopnumber}{2}

@@

\begin{figure*}[t]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic_bounds_lca_windows_beta.pdf}%
\caption{$\beta$-values of the windows LCA selects for each image pixel. The underlying image is the one shown in \Fig{oversampling_mosaic_bounds}, and the location of the anchor and cut line is overlaid. }\label{oversampling_mosaic_bounds_beta}
\end{figure*}

% \setcounter{dbltopnumber}{1}

@@

Adaptive beamformers process each pixel in a different way in an attempt to surpass the conventional limit of resolution and noise suppression. This non-linear processing of the image increases its bandwidth and introduces a need for oversampling. For MVDR often a factor 10 lateral oversampling is often needed to ensure spatial shift-invariance in source amplitude~\cite{Asen2014}. To compare apples to apples, we will use the same factor for both LCA and MVDR.

Need $M$ in the image sector. Why???

- Abs -> adds a factor 2
- log -> infinity?
- near field -> range and azimuth is coupled

@@

\begin{itemize}
\item \emph{Window function}. \Fig{mvdr_selected_windows} show frequency responses of typical windows chosen by MVDR in shadow, speckle and highlight regions in an image. The responses tend to be symmetric, minimally steered and have slightly varying mainlobe width and sidelobe suppression. We use Kaiser windows to mimic these responses.
\item \emph{Window parameters}. The Kaiser window parameter $\beta$ adjusts the compromise between resolution and sidelobe suppression. At $\beta=0$ it yields a rectangular window, and at and $\phi$ controls the amount of steering.. $\beta=0$ ) and a gaussian curve (
\end{itemize}
